Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-03-24 2017-Xudong-SMT/OpenPNets-SMT.tex
More content in "interaction with Z3"
Left - the transition of the predicates
     - the result analysis
     - the conclusion

\paragraph{translation of presentation}
\QIN{
The $datatypes$ are declared according to the $sorts$ the users declared in the $presentation$. Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they will be required if there are new $operators$ declared in the $presentation$. If the return type of the functions is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet. 
}

\paragraph{checking satisfiability}
After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\

>>>>

\paragraph{translation of presentation}
\QIN{
The $datatypes$ are declared according to the $sorts$ the users declared in the $presentation$. If the return type of the $functions$ is one of the $datatypes$, we add this $function$ when declare the $datatypes$, it present the reality that every action expression also belongs to a sort of pNet. Although in Fig~\ref{schema:smt-lib} we have not declared $functions$, they should be exactly declared if there are new $operators$ declared in the $presentation$. The input type of the $function$ can be $Int$, $Bool$ or the $datatypes$ declared all determined by the construct of the  $operators$ in the presentation. For example, we define a new operator to present the equation between two actions in CCS example $\text{EQUAL}$ in the format likes:
}
\[< Action , Action > \rightarrow Bool .\]
\QIN{
It will be translated into the Z3 statement: 
}
\[(declare\text{-}fun\ \text{EQUAL}\ (Action\ Action)\ Bool) .\]

\paragraph{checking satisfiability}
\TODO{After we get the result OTs, for each result OT, declare the variables and assertions in the Java API. Conduct checking method and get the result.\\}
